%\documentclass[iop,revtex4]{emulateapj}% change onecolumn to iop for fancy, iop to twocolumn for manuscript
\documentclass[twocolumn]{emulateapj}% change onecolumn to iop for fancy, iop to onecolumn for manuscript
%\documentclass[12pt,preprint]{aastex}

%\usepackage{lineno}
%\usepackage{blindtext}
%\linenumbers

\let\pwiflocal=\iffalse \let\pwifjournal=\iffalse
%From: http://arxiv.org/format/1512.00483
%\input{setup}
\input{mgs_setup}


\newcommand{\iancze}{{\sc C15}}

\providecommand{\eprint}[1]{\href{http://arxiv.org/abs/#1}{#1}}
\providecommand{\adsurl}[1]{\href{#1}{ADS}}
\newcommand{\name}{LkCa 4 }
\newcommand{\project}[1]{\textsl{#1}}
%\def\vsini{$v\sin{i_*}$}


\slugcomment{In preparation}

\shorttitle{Extreme Starspots in Taurus}

\shortauthors{Gully-Santiago et al.}

\bibliographystyle{yahapj}

\begin{document}

\title{The coverage fraction of starspots on young Taurus members and consequences for stellar ages estimates at 1$-$10 Myr}

\author{Michael A. Gully-Santiago,\altaffilmark{1}, author list TBD}


\altaffiltext{1}{Kepler/K2 Guest Observer Office, NASA Ames Research Center, Moffett Field, CA, USA}

\begin{abstract}

We assess starspot temperatures and coverage fraction for three heavily spotted Taurus pre-main sequence young stellar objects from their high-resolution, high bandwidth near infrared IGRINS spectroscopy.  We forward model the spectra with a mixture of cool and hot photosphere components using the \texttt{Starfish} spectral inference framework.  The disk-free, non-accreting sample members have 10$-$30 years worth of polychomatic photometry, which we use in four ways: first, to register the acquisition time of the spectroscopic measurement to the stellar rotational phase; second, to derive the secular changes of areal coverage fraction over 1 to 30 year timescales; third, to derive rotation periods; and fourth, to assign lower-limits to areal filling factors based on the amplitude of photometric variation and limiting case of non-emitting equatorial spots.  We derive starspot temperatures in the range of $x$ to $y$ K, and filling factors of $v$ to $z$.  These filling factors are typically $k$ to $m$ times higher than the limiting case of non-emitting equatorial spots, implying that either the stars possess large circumpolar starspots with the stellar spin axis inclined moderately towards our reference frame, or that the stars possess three or more dominant temperature components, rendering our two-temperature retrieval process flawed.  The filling factors and temperatures cause effective temperature estimates to systematically decrease, confounding age and mass estimates of these young stars and by extension all previous spectral-type-based estimates of fundamental properties of heavily spotted stars, though more work is needed.  The observations of secularly varying photometric amplitudes are consistent with the physical interpretations that some or all young stars pass through short-lived phases of enhanced starspot coverage, or that starspots migrate from near the poles towards the equator over time.

\end{abstract}

\keywords{stars: fundamental parameters ---  stars: low-mass --- stars: statistics}

\maketitle

\section{Introduction}\label{sec:intro}

The evolutionary state of a star can be superbly predicted with an age and a mass.  Angular momentum and metallicity further improve those predictions.  Unfortunately the age of a star cannot be trivially measured.  Pre-main sequence isochronal methods provide only coarse estimates of cluster ages, with perhaps 100\% uncertainties attributable to both intrinsic scatter and systematic bias.  Isochronal models generally ignore angular momentum, a safe bet after stars have resided on the pre-main-sequence for much longer than their formation timescale.  Pre-main sequence stars differ.  For the first $1-100$ Myr of a star's life, the rotation rate of a star may inhibit convective efficiency, making the star dwell in its puffed-up, larger-than-expected radius, in order to allow the same amount of internal energy to escape.  The extra-high rotation rates of young stars interplay with both global and surface magnetic fields and environmental factors to yield complex evolutionary phenomena.

One observational manifestation of rotationally-heightened magnetic fields is the presence of \emph{starspots}.  Starspots serve as a familiar---albeit inexact---avenue through which we can quantify possible limitations to isochronal age estimates.  Importantly, starspots possess many favorable observational properties that form the central thrust of this paper.  In our previous paper \citep{2017ApJ...836..200G}, we combined multiple datasets to reveal a large $\sim75\%$ coverage fraction of starspots on the surface of the Weak-Lined T-Tauri Star (WTTS) LkCa~4.  Here we seek to identify whether LkCa~4 merely represents an extreme outlier, or whether other WTTS's can possess similiarly large starspots.


We first emphasize possible geometric degeneracies that can give rise to larger-than-expected starspots.  We then collate numerous photometric and spectroscopic data sources (Section XXX), and their starspot-centric analyses (Section XXX).  We combine inferences on our small sample of stars to assess the effect of starspots on the pre-main sequence HR-diagram (Section XXX).  Finally we question our initial assumptions in Section XXX.

\section{Observations}\label{sec:obs}




\subsection{IGRINS Spectroscopy}\label{sec:igrins}

Recently, \citet{2017ApJ...836..200G} found evidence for a large starspots on the Weak-Lined T-Tauri Star LkCa 4.
Here are some citations:

IGRINS \citep{park14}

The data were reduced with the Pipeline Package \citep{jaejoonlee15}.

\subsection{Photometric monitoring}

We used photometry from \citep{grankin08}.


ASAS3 \citep{pojmanski04}?

Integral-OMC \citep{garzon12}?

The AAVSO archive \citep{kafka16}?

Unpublished data from the ASAS-SN survey \citep{shappee14}, yes!


Multiterm Lomb-Scargle periodograms \citep{ivezic14}, and fourier series truncated to the first $\sim 4$ components]{vanderplas15a}.

2MASS \citep{skrutskie06}.

\section{FITS TO HIGH RESOLUTION SPECTRA}\label{sec:Starfish}


\subsection{Methodology}\label{sec:methods}

Of course we need! \citet[hereafter \iancze]{czekala15}
yay!

Phoenix woo!: \citep{husser13}.

Somers woo!: \citep{somers15}.

We use \texttt{emcee} \citep{foreman13}.


\section{Conclusions}

Yay, we did it!

\clearpage
\pagebreak


\appendix

\section{Are starspots confusing?}
\label{methods-details}

Short answer: no!

\acknowledgements

We thank ADS!


{\it Facilities:} \facility{Smith (IGRINS)}, \facility{AAVSO}, \facility{CFHT (ESPaDOnS)}, \facility{INTEGRAL (OMC)}, \facility{ASAS}, \facility{CrAO:1.25m}, \facility{ARC (TripleSpec)}, \facility{Hale (DBSP)}, \facility{Gaia}

{\it Software: }
 \project{pandas} \citep{mckinney10},
 \project{emcee} \citep{foreman13},
 \project{matplotlib} \citep{hunter07},
 \project{numpy} \citep{vanderwalt11},
 \project{scipy} \citep{jones01},
 \project{ipython} \citep{perez07},
 \project{gatspy} \citep{JakeVanderplas2015},
 \project{starfish} \citep{czekala15},
 \project{seaborn} \citep{waskom14}
%\software{%
% \project{pandas} \citep{mckinney10}
%    \project{emcee} \citep{foreman13},
% \project{matplotlib} \citep{hunter07},
% \project{numpy} \citep{vanderwalt11},
% \project{scipy} \citep{jones01},
% \project{ipython} \citep{perez07},
% \project{gatspy} \citep{JakeVanderplas2015},
% \project{starfish} \citep{czekala15}}.

\clearpage

\bibliographystyle{apj}
\bibliography{ms}

\end{document}
